---
title: "PubChem JSON API"
output: html_notebook
editor_options: 
  chunk_output_type: console
---

```{r knitr, echo=FALSE}
knitr::opts_knit$set(root.dir = normalizePath(".."))
```

```{r install.packages, echo=FALSE, eval=FALSE}
install.packages("RCurl")
install.packages("rjson")
install.packages("rvest")
install.packages("data.table")
install.packages("tidyverse")
install.packages("stringr")
install.packages("devtools")
```

```{r}
library(devtools)
```

```{r, echo=FALSE, eval=FALSE}
devtools::install_github(repo = "data.tree", username = "gluc")
```

```{r load.packages, echo=FALSE}
library(RCurl)
library(jsonlite)
library(rvest)
library(data.tree)
library(data.table)
library(stringr)
library(tidyverse)
```

```{r source.pubchem.parse}
source("lib/pubchem_parse.R")
```


# Pubchem PUG URL's

Most, if not all, of the information the service needs to produce its results is encoded into the URL. The general form of the URL has three parts – input, operation, and output – after the common prefix, followed by operation options as URL arguments (after the ‘?’):

`https://pubchem.ncbi.nlm.nih.gov/rest/pug/<input specification>/<operation specification>/[<output specification>][?<operation_options>]`

```{r}
compound.id <- "6618"
```


```{r}
# Import JSON for compound
compound.url <- paste0("https://pubchem.ncbi.nlm.nih.gov/rest/pug_view/data/compound/",
                       compound.id,
                       "/JSON/?response_type=save$response_basename=CID_",
                       compound.id)

compound.tree <- compound.url %>%
                  read_json() %>%
                  FromListSimple()
```

```{r compound.tree.prune}
compound.tree <- compound.tree$Record$Section
```

```{r initialize.empty.tables}
master.count <- data.table()
master.text <- data.table()
```

# Sections to scrape
* CACTVS String
* Pharmacology and Biochemistry
    + Pharmacology
    + Absorption, Distribution, and Excretion
    + Metabolism/Metabolites
    + Biological Half-Life
    + Mechanism of Action
    + Human Metabolite Information
        - Metabolite Description
        
* Use and Manufacturing
* Identification
* Safety and Hazards
* Toxicity
* PubMed Citations
* Patents
* Biosystems and Pathways
* BioAssay Results

# Compound Name

```{r}
compound.name <- compound.tree$Climb(TOCHeading = "Names and Identifiers")$Section$`1`$Information$`1`$StringValue
```


# CACTVS String
```{r}
chem.phys.prop <- compound.tree$Climb(TOCHeading = "Chemical and Physical Properties")$Section
```

```{r}
cactvs <- chem.phys.prop$Climb(TOCHeading = "Computed Properties")$Information
```


# Pharmacology and Biochemistry
```{r pharm.bio}
pharm.bio <- compound.tree$Climb(TOCHeading = "Pharmacology and Biochemistry")$Section
```

## Pharmacology

```{r pharmacology}
pharmacology <- ScrapeSection(pharm.bio, "Pharmacology")
```

## Absorption, Distribution, and Excretion

```{r absorption_distribution_excretion}
absorption <- ScrapeSection(pharm.bio, "Metabolism/Metabolites")

# absorption <- Clone(pharm.bio$Climb(TOCHeading = "Absorption, Distribution and Excretion")$Information)
# absorption <- absorption$Get("StringValue", filterFun = function(x) {x$level == 2})
# absorption.text <- CollapseTextVector(absorption)
# absorption <- str_count(absorption.text, "\\S+")
```

## Biological Half-Life

```{r}
half.life <- pharm.bio$Climb(TOCHeading = "Biological Half-Life")$Information$Get("StringValue")
```

## Mechanism of Action

```{r}
mechanism <- pharm.bio$Climb(TOCHeading = "Mechanism of Action")$Information$Get("StringValue")
mechanism <- mechanism[!is.na(mechanism)]
mechanism.text <- CollapseTextVector(mechanism)
mechanism <- str_count(mechanism.text, "\\S+")
```


```{r}
mechanism_of_action <- aspirin_pharm_bio$Section$Climb(TOCHeading = "Mechanism of Action")
```


```{r}
aspirin_literature <- aspirin_$Climb(TOCHeading = "Literature")
```

```{r}
aspirin_literature$Get(attribute = "TOCHeading")
```

```{r}
aspirin_nature_references <- aspirin_literature$Section$Climb(TOCHeading = "Springer Nature References")
```

```{r}
i <- 2244
df_csv <- fread(paste0("https://pubchem.ncbi.nlm.nih.gov/sdq/sdqagent.cgi?infmt=json&outfmt=jsonp&query=%5B%7B%22download%22:%5B%22pmid%22%5D,%22collection%22:%22pubmed%22,%22where%22:%7B%22ands%22:%5B%7B%22cid%22:%22", i, "%22%7D%5D%7D,%22order%22:%5B%22relevancescore,desc%22%5D,%22start%22:1,%22limit%22:1000000%7D,%7B%22histogram%22:%5B%22articlepubdate%22%5D%7D%5D"))
```


# Testing pubchem_parse.R

```{r}
source(file = "../lib/pubchem_parse.R")
pubchemparse.test <- PubChemParse(c("6618", "2244", "22286931"), NULL, db.bypass = TRUE)
```

